\section{Purpose/Vision}
%Provide a clear, short and sweet vision for your team and your product

The product owner, Leapkit, wants a matchmaking algorithm for their webportal, matching students with projects uploaded by companies to their site. Student information will be gathered from their LinkedIn profile. The matchmaking algorithm should match on the students skills and requirements set by the companies.

We want to create the integration with LinkedIn, and produce the mathmaking algorithm and integrate it into the existing Leapkit solution.

%We want to produce and implement the ``\emph{matchmaking-algorithm}''
%that can help Leapkit match companies/projects to students with relevant
%skills and interests based on their LinkedIn profile. The LinkedIn %information will be gathered by integrating LinkedIn via its API.

\subsection{Roadmap}
%Briefly outline your intended product including sprint goals for each sprint
%and initial product backlog
\begin{itemize*}
  \item Sprint 1
        \begin{enumerate*}
          \item Preliminary implementation of authentication with LinkedIn.
          \item Preliminary implementation of information retrieval from LinkedIn.
          \item Overall design for an algorithm for matching students with projects.
        \end{enumerate*}
  \item Sprint 2
        \begin{enumerate*}
          \item Information retrieval from Leapkit (Django aclimatization).
          \item Finish algorithm design based on information retrieval from Leapkit and LinkedIn.
        \end{enumerate*}
  \item Sprint 3
        \begin{enumerate*}
          \item Implement matchmaking algorithm.
          \item Implement LinkedIn authentication in Leapkit source.
        \end{enumerate*}
  \item Sprint 4
        \begin{enumerate*}
          \item Integrate LinkedIn scraper in Leapkit source.
          \item Integrate matchmaking algorithm in Leapkit source.
          \item Adjustment and finetuning of matchmaking algorithm.
        \end{enumerate*}
  \item Sprint 5
        \begin{enumerate*}
          \item Final adjustments of matchmaking algorithm.
          \item Testing and Quality Assurance.
          \item Final integration and deployment.
        \end{enumerate*}
\end{itemize*}
