\section{Team processes}
%Describe team operational plans. This includes, for example, such activities as the team’s decision-making processes, how changes in membership occur should the need arise, plans to establish “ground” or operating rules, relationships with other organizational entities or teams, logistical support, etc.

Decision-making is done individually and noted on the upcomming work-daily Scrum meeting where the team can discuss and comment on it, which might change the decision. This is subject to change, if it results in too long meetings. It might change to a decision made by the individual and the Scrum master instead, to avoid wasting time of the team as a whole.

Generally all team-oriented problems are handled at the work-daily Scrum meetings.

\subsection{Configuration management}
All progress, i.e. the report and code, will be stored on Github in a private repository.
The report will be written in \LaTeX.
All code pushed to the Git-repository must be able to compile, this include \TeX-files and implementation.
Everything will be written in English, both comments in the code and the reports.

All Scrum related work will be placed in the corresponding sprint report, except the backlog. The backlog will be handled via Github Milestones, and each backlog item as Github issues. Everyone is allowed to edit this. This is subject to change. At the end of each sprint, this will be added to the report of the sprint.

To access the repository one must have a Github account and must contact Martin (See Table \ref{tab:contacts}) with username to get access.

\todo[inline]{The rest is dependant on the internal workings of Leapkit.}

\subsection{Office rules}
We don't work in an office, but will be working primarily at DIKU and if needed at the team members apartments. There will not be strict rules for e.g. the use of phones or small procrastinations like Facebook or personal mails, it is frowned upon however to not help the team reach the goals of the sprint. This will be tightened, if the team does not perform well under these lose constrictions.

\subsection{Calendar planning}

\todo[inline]{Do for real maybe :P}
\begin{table}
    \centering
    \begin{tabular}{l|l|l}
        \rowcolor{Gray}
        \textbf{Activity} & \textbf{When} & \textbf{Where}\\\hline
         Complete goals   & All the time  & All over.
    \end{tabular}
    \label{tab:planning}
\end{table}
