\documentclass{article}

\begin{document}

\section*{Backlog}

% Python connect example: https://github.com/ozgur/python-linkedin/tree/master/linkedin
\begin{itemize}
    \item {T 2:} Create code that can connect to LinkedIn.
    \item {T 2:} Create a (simple, non-intergrated) login portal to let the user provide their linkedin credentials/API-key. 
    \item {T 3:} Create code that can extract information from LinkedIn.
    \item {T 3:} Create code that can translate extracted LinkedIn information into Leapkit information.
    \item {T 4:} Information retrieval from Leapkit.
    \item {T 2:} Create code that can save the translated LinkedIn data to the Leapkit Database.
    \item {T 4:} Research matching methods for the algorithm.
    \item {T 2:} Create pseducode for the matching algorithm.
    \item {T 1:} Finish algorithm design based on information retrieval from Leapkit and LinkedIn.
    \item {T 0-3:} Final adjustments of matchmaking algorithm. - Kasper foreslår det er en catch-all for ændringer til algoritmen.
    \item {T 4:} Implement LinkedIn authentication in Leapkit source.
    \item {T 5:} Integrate LinkedIn information retrieval in Leapkit source.
    \item {T 4:} Implement matchmaking algorithm.
    \item {T 4?:} Integrate matchmaking algorithm in Leapkit source.
    \item {T 0-4:} Adjustment and finetuning of matchmaking algorithm.
    \item {T 0-5:} Final integration and deployment.
    \item {T ?:} Testing and Quality Assurance.
\end{itemize}
\end{document}
