\section{Sprint Goal}

%TODO Report on the sprint goal by describing your current development process and by discussing how and why you have improved/will improve the proces.

The developement process is roughly as follows. A set of tasks are created from a set of sprint goals, whereby the sprint goals are split into smaller, more concrete tasks, typically solvable by one or two developers. The tasks are then given a time frame using Scrum techniques such as planning poker, and afterwards assigned to the developers. This is done by the Scrum master via dialog and in agreement in the team. 

A task is then solved a developer (or a team of developer if needed), and the results are loosely presented to the rest of the team, so everybody is up to date on the current progress. The task is then moved to either the Done list or the Need Testing/Review list, for further testing or reviewing, before either improving/changing the solution based on the review or move it to Done, if the tests where successful.

Thus far, the test and review part of the development process has been very light and of little focus. This can be improved by e.g. forcing other developers, i.e. not the ones who produced the solution, to test/review the solution. Not only will this force the team to focus on quality ensurance and making intelligent solutions, it might also affect the quality of the tests. A tester, who has no knowledge of how the solution works, is not affected by the ideas and assumptions behind this solution and might create testing scenarios covering cases the producing developer had not thought of.

